### 2025-06-09 basic-statistics.qmd
20250609 - coefficient of variation

- standard deviation
- variance
- range
- minimum and maximum
- interquartile range (IQR)
- median absolute deviation

@@

@@

@@

player_stats_seasonal %>% 
  dplyr::select(age, years_of_experience, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

>>>>

- standard deviation
- variance
- range
- minimum and maximum
- interquartile range (IQR)
- median absolute deviation
- coefficient of variation

@@

The coefficient of variation (CV) accounts for the fact that variables with larger means also tend to have larger standard deviations; it is calculated as the standard deviation divided by the mean, as in @eq-coefficientOfVariation:

$$
\text{CV} = \frac{SD(x)}{\bar{x}}
$$ {#eq-coefficientOfVariation}

where $SD(x)$ is the standard deviation of $x$.

@@

- coefficient of variation:

```{r}
sd(player_stats_seasonal$fantasyPoints, na.rm = TRUE) / mean(player_stats_seasonal$fantasyPoints, na.rm = TRUE)
```

@@

player_stats_seasonal %>% 
  dplyr::select(age, years_of_experience, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        CV = ~ sd(., na.rm = TRUE) / mean(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

### 2025-06-09 player-evaluation.qmd
20250609 - coefficient of variation

However, the players differ considerably in their uncertainty (i.e., the source-to-source variability in their projections), as operationalized with the standard deviation and coefficient variation of projected points across sources for a given player.

>>>>

However, the players differ considerably in their uncertainty (i.e., the source-to-source variability in their projections), as operationalized with the [standard deviation](#sec-descriptiveStatisticsSpread) and [coefficient of variation](#sec-descriptiveStatisticsSpread) of projected points across sources for a given player.
